---
title: "Individual Task 1 – Fonterra Social Media Analysis"
author: "Sheikh Mohammad Milton, ID No. 1713714"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    df_print: paged
---

# 1. Introduction

## 1.1 Purpose of the analysis

This assignment analyses Fonterra's social media content to identify the main topics discussed across its official social media accounts and to examine user engagement with that content. The analysis uses the supplied `fonterra.csv` dataset and is completed in R.

The analysis includes data preparation, term-frequency analysis, topic modelling, exploratory data analysis, bivariate statistical analysis, and data-informed recommendations.

## 1.2 Load packages

```{r initial}
# Install and load packages
if(!require("pacman"))install.packages("pacman")
pacman::p_load(readr, dplyr, tidyr, stringr, lubridate, purrr, ggplot2, gridExtra, GGally, corrplot)
pacman::p_load(tidytext, textstem, wordcloud, textdata, topicmodels)
pacman::p_load(DescTools, skimr, finalfit, rstatix, huxtable, jtools)
pacman::p_load(knitr, easystats, gtsummary, gt, scales)

```

# 2. Data Import and Initial Inspection

## 2.1 Import the dataset

```{r Import Data}
# Import and preview data
data_raw <- read_csv("fonterra.csv", locale = locale(encoding = "ISO-8859-1"), show_col_types = FALSE)

```

## 2.1 Initial Inspection

```{r Initial Inspection}
# Display the dimensions of the dataset
dim(data_raw)

# Inspect the variable names and data types
glimpse(data_raw)

# Display the first 10 rows
head(data_raw, 10)

# Display distinct values
unique(data_raw$platform)
unique(data_raw$media)

# Checking decimal value in count variables
data_raw |>
  summarise(across(where(is.numeric), ~ any(.x %% 1 != 0, na.rm = TRUE)))
```

## 2.2 Dataset overview

```{r dataset-overview}
# Create a compact overview of the dataset.
overview <- tibble(
  item = c("Number of observations", "Number of variables",
           "Number of platforms", "Number of unique URLs"),
  value = c(
    nrow(data_raw),
    ncol(data_raw),
    n_distinct(data_raw$platform),
    n_distinct(data_raw$url)
  )
)

kable(overview, caption = "Overview of the Fonterra dataset")

rm(overview)
```

```{r platform-counts}
# Count observations by social media platform
platform_counts <- data_raw |>
  count(platform, sort = TRUE)

kable(platform_counts, caption = "Number of observations by platform")

# Count observations by media
media_counts <- data_raw |>
  count(media, sort = TRUE)

kable(media_counts, caption = "Number of observations by media")

rm(platform_counts, media_counts)
```

## 2.3 Missing values

```{r missing-values}
# Count missing values in each variable.
missing_summary <- data_raw |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "missing_count"
  ) |>
  mutate(
    missing_percent = missing_count / nrow(data_raw) * 100
  ) |>
  arrange(desc(missing_count))

kable(
  missing_summary,
  digits = 2,
  caption = "Missing values by variable"
)

rm(missing_summary)
```

**Observation:**

i) Dataset under review has 9001 rows/ observations against 9 columns/ variables

ii) Data Type:

Character: platform, url, createdAt, text and media
Number: commentCount, shareCount, shareCount, likeCount and videoplayCount

iii) For better and accurate analysis, we must transform existing data type to their actual data format. We must transform:

a) platform and media to categorical data type
b) createdAt to DATE data type
c) commentCount, shareCount, likeCount and videoplayCount to INTEGER data type

iv) Maximum missing values exists in videoplayCount. This is natural since there may have several posts which don't have any video content

v) 6994 observations have no specified media and there exists naming difference in media. It shows video and Video in separte category although the main difference exist in first letter. Also Photo, Image and image are same type media. So, adjustment is required to align this ambiguities.

# 3. Data Preparation

## 3.1 Non-text data

### 3.1.1 Date and Time

The createdAt variable is converted to a date-time variable. Separate year, month and day-of-week variables are also created for later analysis.

```{r req_2a}
# Convert createdAt to a date-time variable and create useful time variables
data <- data_raw |>
  mutate(
    created_datetime = ymd_hms(createdAt, quiet = TRUE, tz = "UTC"),
    year = year(created_datetime),
    month = month(created_datetime, label = TRUE, abbr = TRUE),
    day_of_week = wday(created_datetime, label = TRUE, abbr = TRUE, week_start = 1)
  )

# Check maximum and minimum year and whether any dates failed to convert
print(min(year(data$created_datetime), na.rm = TRUE))
print(max(year(data$created_datetime), na.rm = TRUE))
sum(is.na(data$created_datetime))

```

**Observation:**

i) We have data/ observations  ranging from the year 2010 to 2026
ii) There exists no data failed to convert

### 3.1.2 Number Data

The commentCount, shareCount, likeCount and videoplayCount variables are converted to integer number

```{r}
# Converting commentCount, shareCount, likeCount and videoplayCount variables to integer number
data <- data |>
  mutate(across(
    c(commentCount, shareCount, likeCount, videoplayCount), 
    as.integer
  ))

# View data types and see if NA values are still present
summary(data[c("commentCount", "shareCount", "likeCount", "videoplayCount")])
```

## 3.2 CATEGORICAL data

### 3.2.1 Converting to CATEGORICAL data

```{r}
# Converting platform and media variables to categorical data type
data$platform <- as.factor(data$platform)
data$media <- as.factor(data$media)
```

### 3.2.2 Standardised media categories

The `media` variable contains inconsistent capitalisation such as `Video` and `video`, and `Image` and `image`. These values are standardised into consistent categories.

**Data-preparation judgement:** `Photo` and `Image` are treated as the same broad media category, and `Video` and `video` are treated as the same category because the difference is only capitalisation/ label wording. Missing media values are retained as `No media recorded` rather than assumed to represent a particular media format.

```{r media-preparation}
# Standardise media labels while retaining missing media information.
data <- data |>
  mutate(
    media_type = case_when(
      is.na(media) ~ "No media recorded",
      str_to_lower(media) %in% c("photo", "image") ~ "Image",
      str_to_lower(media) == "video" ~ "Video",
      str_to_lower(media) == "sidecar" ~ "Sidecar",
      TRUE ~ "Other"
    ),
    media_type = factor(
      media_type,
      levels = c("No media recorded", "Image", "Video", "Sidecar", "Other")
    )
  )

data |>
  count(media_type, sort = TRUE) |>
  kable(caption = "Standardised media categories")
```


## 3.3 Create new variables

### 3.3.1 Creating Social Engagement variable

**Judgement:** Missing comments and shares are not automatically interpreted as zero in the original variables. For the derived `social_engagement` measure, `coalesce()` is used so that the measure can be calculated, while the original missing values remain available for inspection. `videoplayCount` is not included in this combined measure because video plays are conceptually different from likes, comments and shares

```{r engagement-preparation}
# Missing values in commentCount, shareCount and likeCount variables are treated as zero which means no social interaction. Zero means no interaction

# Create indicators and a social-engagement measure. Likes, comments and shares are treated as direct social interactions. Video plays are kept separate because they represent consumption rather than the same type of interaction

data <- data |>
  mutate(
    social_engagement =
      coalesce(likeCount, 0) +
      coalesce(commentCount, 0) +
      coalesce(shareCount, 0),
    has_video_plays = !is.na(videoplayCount) & videoplayCount > 0,
    has_media = media_type != "No media recorded"
  )

summary(data$social_engagement)
```

### 3.3.2 Text length and word count

**Judgement:** `text_length` and `word_count` can be used to investigate whether longer posts are associated with different engagement levels.

```{r text-variables}
data <- data |>
  mutate(
    text_clean_for_length = replace_na(text, ""),
    text_length = str_length(text_clean_for_length),
    word_count = str_count(
      str_squish(text_clean_for_length),
      "\\S+"
    )
  )

summary(data |> select(text_length, word_count))
```

### 3.3.3 Video-content indicator

**Judgement:** `media_type`, `has_media`, and `is_video` allow engagement to be compared across different content formats.

```{r video-indicator}
# Create a simple indicator for content that is explicitly identified as video.
data <- data |>
  mutate(
    is_video = media_type == "Video"
  )

data |>
  count(is_video) |>
  mutate(percent = n/sum(n) * 100) |>
  kable(digits = 2, caption = "Video and non-video observations")
```

## 3.4 Checking duplicate records

**Data-preparation judgement:** Duplicate records should not be removed automatically without checking their meaning. In this dataset, URLs are checked first because the URL is a useful content identifier. If duplicate observations are identified, their content and timestamps should be reviewed before deciding whether they represent repeated content or data errors.

```{r duplicates}
# Check for duplicated URLs and completely duplicated rows
duplicate_url_count <- sum(duplicated(data$url))
duplicate_row_count <- sum(duplicated(data))

tibble(
  duplicate_type = c("Duplicated URLs", "Duplicated complete rows"),
  count = c(duplicate_url_count, duplicate_row_count)
) |>
  kable(caption = "Duplicate record checks")

rm(duplicate_url_count, duplicate_row_count)
```


```{r remove-exact-duplicates}
# Remove only completely duplicated rows.This is a conservative choice because identical URLs do not necessarily mean that the records are errors.
data <- data |>
  distinct()
```

** No duplicate records found **

# 4. Text Data Preparation

## 4.1 Prepare text for analysis

The `text` variable is prepared for term-frequency analysis and topic modelling. URLs, punctuation, numbers and common stop words are removed. The text is converted to lower case and tokenised into individual words.

```{r text-cleaning}
custom_stopwords <- tibble(
  word = c("https", "http", "www", "com",
           "fonterra", "nz", "new", "zealand"),
  lexicon = "custom"
)

stop_words <- bind_rows(stop_words, custom_stopwords)

clean_ngram <- function(data, n_size, col_name) {
  data |>
    unnest_tokens(!!sym(col_name), text, token = "ngrams", n = n_size) |>
    filter(
      str_detect(!!sym(col_name), paste0("^([a-z]+ ){", n_size - 1, "}[a-z]+$")),
      !str_detect(!!sym(col_name), "\\bhttps?\\b")
    ) |>
    filter(
      map_lgl(str_split(!!sym(col_name), " "), ~ !any(.x %in% stop_words$word))
    )
}

# Create a text dataset and remove missing/blank text.
text_data <- data |>
  select(url, platform, text) |>
  mutate(text = replace_na(text, "")) |>
  filter(str_squish(text) != "") |>
  mutate(document = row_number())

# Tokenise text into ngrams up to n = 1 to 6
uni_clean      <- clean_ngram(text_data, 1, "word")
bigram_clean   <- clean_ngram(text_data, 2, "bigram")
trigram_clean  <- clean_ngram(text_data, 3, "trigram")
quadgram_clean <- clean_ngram(text_data, 4, "quadgram")
pentagram_clean <- clean_ngram(text_data, 5, "pentagram")
hexagram_clean  <- clean_ngram(text_data, 6, "hexagram")

rm(clean_ngram, custom_stopwords, text_data, stop_words)

```

## 4.2 Observing most frequent words

```{r text-cleaning}
# Observing most frequent words
# Combine datasets and metadata into a structured list
ngram_list <- list(
  list(data = uni_clean, col = "word", name = "one word"),
  list(data = bigram_clean, col = "bigram", name = "two word"),
  list(data = trigram_clean, col = "trigram", name = "three word"),
  list(data = quadgram_clean, col = "quadgram", name = "four word"),
  list(data = pentagram_clean, col = "pentagram", name = "five word"),
  list(data = hexagram_clean, col = "hexagram", name = "six word")
)

# Generate all tables in a single operation
purrr::walk(ngram_list, function(ng) {
  ng$data |>
    count(!!sym(ng$col), sort = TRUE) |>
    slice_head(n = 30) |>
    kable(caption = paste("Initial most frequent", ng$name, "terms")) |>
    print()
})

```

## 4.3 Stemming and Lemmatisation
Depending on the data, stemming and lemmatisation has been performed to improve usability of the output, make no difference, or lead to incorrect conclusions if the meaning of the words diverts too much from their original meaning.

```{r}
# Unigram
## Stem and lemmatise words
uni_sl <- uni_clean |>
  mutate(uni_stem = stem_words(word),
         uni_lemma = lemmatize_words(word))

## Comparison of the original, stemmed, and lemmatised forms
g1 <- uni_sl |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g2 <- uni_sl |>
  count(uni_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(uni_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g3 <- uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(uni_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g1, g2, g3, ncol = 3)

## Keep lemmatised form and override object
uni_clean <- uni_sl |>
  select(-c(word, uni_stem)) |>
  rename(word = uni_lemma)

# Bigram
## Stem and lemmatise bigrams
bi_sl <- bigram_clean |>
  mutate(bigram_stem = stem_strings(bigram),
         bigram_lemma = lemmatize_strings(bigram))

## Comparison of the original, stemmed, and lemmatised forms
g4 <- bi_sl |>
  count(bigram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g5 <- bi_sl |>
  count(bigram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g6 <- bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g4, g5, g6, ncol = 3)

## Keep lemmatised form and override object
bi_clean <- bi_sl |>
  select(-c(bigram, starts_with("word"), contains("stem"))) |>
  rename(bigram = bigram_lemma)

# Trigram
## Stem and lemmatise Trigrams
tri_sl <- trigram_clean |>
  mutate(trigram_stem = stem_strings(trigram),
         trigram_lemma = lemmatize_strings(trigram))

## Comparison of the original, stemmed, and lemmatised forms
g7 <- tri_sl |>
  count(trigram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g8 <- tri_sl |>
  count(trigram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g9 <- tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g7, g8, g9, ncol = 3)

## Keep lemmatised form and override object
tri_clean <- tri_sl |>
  select(-c(trigram, starts_with("word"), contains("stem"))) |>
  rename(trigram = trigram_lemma)

# Quadgram
## Stem and lemmatise Quadgrams
quad_sl <- quadgram_clean |>
  mutate(quadgram_stem = stem_strings(quadgram),
         quadgram_lemma = lemmatize_strings(quadgram))

## Comparison of the original, stemmed, and lemmatised forms
g10 <- quad_sl |>
  count(quadgram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g11 <- quad_sl |>
  count(quadgram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g12 <- quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g10, g11, g12, ncol = 3)

## Keep lemmatised form and override object
quad_clean <- quad_sl |>
  select(-c(quadgram, starts_with("word"), contains("stem"))) |>
  rename(quadgram = quadgram_lemma)

# Pentagram
## Stem and lemmatise Fivegrams
penta_sl <- pentagram_clean |>
  mutate(pentagram_stem = stem_strings(pentagram),
         pentagram_lemma = lemmatize_strings(pentagram))

## Comparison of the original, stemmed, and lemmatised forms
g13 <- penta_sl |>
  count(pentagram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g14 <- penta_sl |>
  count(pentagram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g15 <- penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g13, g14, g15, ncol = 3)

## Keep lemmatised form and override object
penta_clean <- penta_sl |>
  select(-c(pentagram, starts_with("word"), contains("stem"))) |>
  rename(pentagram = pentagram_lemma)

# Hexagram
## Stem and lemmatise Sixgrams
hexa_sl <- hexagram_clean |>
  mutate(hexagram_stem = stem_strings(hexagram),
         hexagram_lemma = lemmatize_strings(hexagram))

## Comparison of the original, stemmed, and lemmatised forms
g16 <- hexa_sl |>
  count(hexagram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g17 <- hexa_sl |>
  count(hexagram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g18 <- hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g16, g17, g18, ncol = 3)

## Keep lemmatised form and override object
hexa_clean <- hexa_sl |>
  select(-c(hexagram, starts_with("word"), contains("stem"))) |>
  rename(hexagram = hexagram_lemma)


rm(g1, g2, g3, g4, g5, g6, g7, g8, g9, g10, g11, g12, g13, g14, g15, g16, g17, g18, bi_clean, ngram_list, bigram_clean, tri_clean, trigram_clean, quad_clean, quadgram_clean, penta_clean, pentagram_clean, hexa_clean, hexagram_clean)

```

# 5. What Topics Have Content Creators Been Posting About?

## 5.1 Term Frequency Analysis

```{r}
# Calculate term frequencies.
# Unigram
## Word count table
uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(uni_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Unigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
uni_sl |>
  group_by(uni_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = uni_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Bigram
## Word count table
bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(bigram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Bigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
bi_sl |>
  group_by(bigram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = bigram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))
# Trigram
## Word count table
tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(trigram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
tri_sl |>
  group_by(trigram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = trigram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Quadgram
## Word count table
quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(quadgram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
quad_sl |>
  group_by(quadgram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = quadgram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Pentagram
## Word count table
penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(pentagram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
penta_sl |>
  group_by(pentagram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = pentagram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Hexagram
## Word count table
hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(hexagram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
hexa_sl |>
  group_by(hexagram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = hexagram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))
```

## 5.2 Topic Modelling

A Latent Dirichlet Allocation (LDA) model with six topics is fitted as an initial model, following the assignment guidance.

```{r topic-modelling-data}
# Prepare a document-term matrix for topic modelling.
# Documents with no remaining tokens are excluded from the model.
document_terms <- uni_clean |>
  count(document, word, sort = FALSE)

documents_with_tokens <- document_terms |>
  distinct(document)

dtm <- document_terms |>
  cast_dtm(document, word, n)

dim(dtm)
```

```{r lda-model}
# Fit an LDA model with six topics.
set.seed(1234)

lda_model <- LDA(
  dtm,
  k = 6,
  control = list(seed = 1234)
)

lda_model
```

### 5.2.1 Most probable words for each topic

```{r topic-words}
# Extract word probabilities for each topic.
topic_terms <- tidy(lda_model, matrix = "beta")

# Display the ten highest-probability words for each topic.
top_topic_words <- topic_terms |>
  group_by(topic) |>
  slice_max(beta, n = 10, with_ties = FALSE) |>
  arrange(topic, desc(beta))|>
  ungroup()

kable(
  top_topic_words,
  digits = 4,
  caption = "Top ten words by probability for each topic"
)
```

```{r topic-word-plot, fig.width=9, fig.height=8}
# Visualise the most probable words for each topic.
top_topic_words |>
  mutate(
    plot_term = reorder_within(term, beta, topic)
  ) |>
  ggplot(aes(x = plot_term, y = beta)) +
  geom_col() +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered() +
  labs(
    title = "Most Probable Words Within Each Topic",
    x = NULL,
    y = "Word Probability"
  ) +
  theme_minimal()
```

** Observation:**
Figure shows the most probable words associated with each of the six topics identified through the topic modelling analysis. The horizontal bars represent the estimated probability of each word within its corresponding topic, with longer bars indicating a stronger association with the topic.

Topic 1: water, farm(er), people, product(s) — farming/sustainability themed

Topic 2: milk, farmer, business, million, china — financial/milk-price themed

Topic 3: team, milk, cheese, worldmilkday — brand/team themed

Topic 4: team, company, award, day, kid(s) — community/awards themed

Topic 5: milk, farm, product, food — production themed

Topic 6: cheese, cream, dairy, share, award — consumer product themed


```{r}
# Keep only transformed 'data' object
rm(list = setdiff(ls(), "data"))
```

# 6. User Engagement Analysis

## 6.1 Exploratory data analysis

```{r}
# Data preparation

fonterra <- data |>
  mutate(
    platform  = factor(platform),
    media_type  = factor(media_type,
                         levels = c("No media recorded", "Image", "Sidecar", "Video")),
    day_of_week = factor(day_of_week,
                         levels = c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")),
    month = factor(month, levels = month.abb),

# Extra analysis variables
log_engagement = log1p(social_engagement),
engagement_level = factor(
  if_else(social_engagement > median(social_engagement),
          "High", "Low"),
  levels = c("Low", "High")),

media_present = factor(
  has_media, levels = c(FALSE, TRUE),
  labels = c("No media", "Has media")),

video_post    = factor(
  is_video, levels = c(FALSE, TRUE),
  labels = c("Not video", "Video")),

day_type  = factor(
  if_else(day_of_week %in% c("Sat","Sun"), "Weekend", "Weekday"),
  levels = c("Weekday", "Weekend")),

# Replies on X start with an @mention (customer-service style replies)

is_reply = factor(
  str_detect(coalesce(text, ""), "^@"),
  levels = c(FALSE, TRUE), 
  labels = c("Original post", "Reply"))
  )

glimpse(fonterra)

```

### 6.1.1 Descriptive statistics

```{r}
fonterra |>
  select(commentCount, shareCount, likeCount, videoplayCount, social_engagement, text_length, word_count) |>
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c("{mean} ({sd})",
                                     "{median} ({p25}, {p75})",
                                     "{min}, {max}"),
    missing_text = "Missing"
  ) |>
  bold_labels()

```

```{r desc-by-platform}
fonterra |>
  select(platform, social_engagement, likeCount, commentCount, shareCount, text_length, media_type, day_type) |>
  tbl_summary(
    by = platform,
    statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  ) |>
  add_overall() |>
  bold_labels()
```

```{r zero-engagement}
tibble(
  `Posts with zero engagement` =
    percent(mean(fonterra$social_engagement == 0), 0.1),
  `Skewness of engagement`  =
    round(datawizard::skewness(fonterra$social_engagement)$Skewness, 1),
  `Mean`   = round(mean(fonterra$social_engagement), 1),
  `Median` = median(fonterra$social_engagement))|>
  gt()
```

### 6.1.3 Distribution of engagement

```{r dist-engagement}
p1 <- ggplot(fonterra, aes(social_engagement)) +
  geom_histogram(bins = 60, fill = "#2a6f97") +
  labs(title = "Raw engagement (heavily right-skewed)", x = "Engagement", y = "Posts") +
  theme_modern()

p2 <- ggplot(fonterra, aes(log_engagement)) +
  geom_histogram(bins = 40, fill = "#61a5c2") +
  labs(title = "log(1 + engagement)", x = "log(1 + engagement)", y = "Posts") +
  theme_modern()

grid.arrange(p1, p2, ncol = 2)

```

```{r components}
fonterra |>
  summarise(Likes = sum(likeCount, na.rm = TRUE),
            Comments = sum(commentCount, na.rm = TRUE),
            Shares = sum(shareCount, na.rm = TRUE)) |>
  pivot_longer(everything(), names_to = "type", values_to = "total") |>
  mutate(share = total / sum(total)) |>
  ggplot(aes(reorder(type, share), share)) +
  geom_col(fill = "#2a6f97") +
  geom_text(aes(label = percent(share, 1)), hjust = -0.1) +
  coord_flip() +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Composition of total engagement", x = NULL, y = NULL) +
  theme_modern()
```

### 6.1.4 Platform: volume versus engagement

```{r platform-share}
platform_summary <- fonterra |>
  group_by(platform) |>
  summarise(posts = n(),
            total_eng = sum(social_engagement),
            mean_eng = mean(social_engagement),
            median_eng = median(social_engagement),
            .groups = "drop") |>
  mutate(share_posts = posts / sum(posts),
         share_eng   = total_eng / sum(total_eng))

platform_summary |>
  arrange(desc(median_eng)) |>
  gt() |>
  fmt_number(c(mean_eng, median_eng), decimals = 1) |>
  fmt_percent(c(share_posts, share_eng), decimals = 1) |>
  tab_header(title = "Platform summary")

platform_summary |>
  select(platform, `Share of posts` = share_posts, `Share of engagement` = share_eng) |>
  pivot_longer(-platform) |>
  ggplot(aes(platform, value, fill = name)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = c("#e07a5f", "#2a6f97")) +
  labs(title = "Share of posts vs share of engagement", x = NULL, y = NULL, fill = NULL) +
  theme_modern()
```


```{r platform-box}
ggplot(fonterra, aes(reorder(platform, social_engagement, median),
                     social_engagement + 1, fill = platform)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.2) +
  scale_y_log10(labels = comma) +
  coord_flip() +
  labs(title = "Engagement by platform (log scale)", x = NULL, y = "Engagement + 1") +
  theme_modern()
```

### 6.1.5 Content factors: media, replies, text length

```{r media-plots}
ggplot(fonterra, aes(media_type, social_engagement + 1, fill = media_type)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.2) +
  scale_y_log10(labels = comma) +
  labs(title = "Engagement by media type (log scale)", x = NULL, y = "Engagement + 1") +
  theme_modern()

# Media type is confounded with platform: cross-tabulate
fonterra |>
  tbl_cross(row = platform, col = media_type, percent = "row")

# Same comparison within the platforms where media varies
fonterra |>
  filter(platform %in% c("Facebook", "LinkedIn", "Instagram")) |>
  ggplot(aes(media_type, social_engagement + 1, fill = media_type)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.2) +
  scale_y_log10(labels = comma) +
  facet_wrap(~ platform) +
  labs(title = "Media type within platform", x = NULL, y = "Engagement + 1") +
  theme_modern() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```


```{r replies}
# Roughly 40% of X posts are @replies (customer-service style)
fonterra |>
  filter(platform == "Twitter/X") |>
  group_by(is_reply) |>
  summarise(posts = n(),
            median_eng = median(social_engagement),
            mean_eng = round(mean(social_engagement), 1)) |>
  gt() |> tab_header(title = "X: replies vs original posts")
```


```{r text-length}
ggplot(fonterra, aes(text_length + 1, social_engagement + 1)) +
  geom_point(alpha = 0.15, colour = "#2a6f97") +
  geom_smooth(method = "gam", colour = "#e07a5f") +
  scale_x_log10(labels = comma) + scale_y_log10(labels = comma) +
  labs(title = "Engagement vs text length (log-log)",
       x = "Text length (characters) + 1", y = "Engagement + 1") +
  theme_modern()

fonterra |>
  group_by(platform) |>
  summarise(median_text_length = median(text_length),
            max_text_length = max(text_length)) |>
  gt()
```

### 6.1.6 Time factors

```{r time-year}
fonterra |>
  group_by(year) |>
  summarise(posts = n(), median = median(social_engagement),
            mean = mean(social_engagement)) |>
  pivot_longer(c(median, mean)) |>
  ggplot(aes(year, value, colour = name)) +
  geom_line(linewidth = 1) + geom_point() +
  scale_colour_manual(values = c("#e07a5f", "#2a6f97")) +
  labs(title = "Engagement by year", x = NULL, y = "Engagement", colour = NULL) +
  theme_modern()

# Platform mix changes over time (important confounder)
fonterra |>
  count(year, platform) |>
  ggplot(aes(year, n, fill = platform)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = percent) +
  labs(title = "Platform mix by year", x = NULL, y = "Share of posts", fill = NULL) +
  theme_modern()
```

```{r time-dow-month}
p_dow <- fonterra |>
  group_by(day_of_week) |>
  summarise(median = median(social_engagement), n = n()) |>
  ggplot(aes(day_of_week, median)) +
  geom_col(fill = "#2a6f97") +
  labs(title = "Median engagement by weekday", x = NULL, y = "Median") +
  theme_modern()

p_mon <- fonterra |>
  group_by(month) |>
  summarise(median = median(social_engagement)) |>
  ggplot(aes(month, median)) +
  geom_col(fill = "#61a5c2") +
  labs(title = "Median engagement by month", x = NULL, y = "Median") +
  theme_modern()

grid.arrange(p_mon, p_dow, ncol = 2)
```

```{r video-plays}
fonterra |>
  filter(!is.na(videoplayCount)) |>
  ggplot(aes(videoplayCount, social_engagement + 1)) +
  geom_point(alpha = 0.3, colour = "#2a6f97") +
  geom_smooth(method = "lm", colour = "#e07a5f") +
  scale_x_log10(labels = comma) + scale_y_log10(labels = comma) +
  labs(title = "Engagement vs video plays (posts with play counts)",
       x = "Video plays", y = "Engagement + 1") +
  theme_modern()
```

## 6.2 Findings

**Level of engagement.** Engagement is very unevenly distributed. Across 9,001 posts the mean is about 60 interactions but the median is only 5, with about 16% of posts receiving no engagement at all and a maximum of 11,819. The distribution is extremely right-skewed (skewness about 19), so a small number of viral posts pull the mean far above a typical post. Medians and log-transformed values are therefore the honest summary. Likes make up the large majority of interactions; comments and shares are much rarer.

**Platform.** Twitter/X supplies about 69% of posts but only about 8% of total engagement (median 2). Facebook is 16% of posts and about 64% of total engagement. Median engagement is highest on LinkedIn (about 149), Instagram (about 134) and Facebook (about 74), and lowest on YouTube (0) and X (2).

**Media.** Posts with media have far higher median engagement than text-only posts (about 81 vs 3). Media, however, is completely absent for X in this dataset, so part of this gap is a platform effect. Inside Facebook, posts with media still outperform those without (median about 99 vs 49), and video (about 135) beats images (about 72). LinkedIn shows the same direction but a smaller gap.

**Replies on X.** About 40% of X posts are @replies (customer-service style) with a median engagement of 1, compared with 5 for original posts. These dilute the apparent performance of X.

**Text length and time.** Longer posts tend to have higher engagement, but text length also differs sharply by platform (YouTube and LinkedIn are long, X is short). Engagement rises with year, but the platform mix changes over time (LinkedIn and TikTok only start in 2024), so the trend cannot be read as a pure time effect. Weekday and month differences look small in medians.

**Data caveats.** `shareCount` is entirely missing for Instagram and YouTube and `commentCount` is partly missing for Facebook and LinkedIn; `videoplayCount` exists for only 886 posts. Because `social_engagement` is built from these counts, it is understated for platforms that do not report shares. `text_length` has extreme outliers (up to about 39,000 characters), and 82 posts have no text.




# 11. GenAI Declaration

I used ChatGpt, Claude and Copilot AI as a supporting tool during this assignment. The tool was used for brainstorming, understanding R syntax, troubleshooting code, suggesting ways to structure the analysis, and improving explanations.

I used GenAI as a supporting tool rather than as a replacement for my own analysis. I checked the suggested R code against the assignment requirements and ran the code in R using the supplied Fonterra dataset. I also inspected the data, outputs, statistical results, tables and visualisations myself and made the final decisions about data preparation, analysis and interpretation. Where GenAI suggestions were used, I verified that they were appropriate for the variables and statistical techniques covered in the course.