---
title: "Individual Task 1"
output: 
  html_document:
    code_download: TRUE
editor_options: 
  chunk_output_type: console
---

Maintain a tidy and readable R Markdown file that runs without any errors. Annotate your code by including brief descriptions of what the codes do.

*Notes:* 
- You can have separate code chunks within each section if preferred and/or include more subheadings. The `Insert a new code chunk` green button is on the top left corner and subheadings can be defined by hashtags.
- Maintain the main headings that separate the requirements and make sure the codes can run in the order presented.
- Consider completing your text responses in a document editor with spellcheck and then copy and paste the responses into the appropriate location in the RMD file.

# Install and load packages and import and preview data

```{r initial}
# Install and load packages
if(!require("pacman"))install.packages("pacman")
pacman::p_load(readr, dplyr, tidyr, stringr, lubridate, purrr, ggplot2, gridExtra, GGally, corrplot)
pacman::p_load(tidytext, textstem, wordcloud, textdata, topicmodels)
pacman::p_load(DescTools, skimr, finalfit, rstatix, huxtable, jtools)

# Import and preview data


```

# Data preparation

## Non-text data

Brief notes on judgement applied:

< (Delete this line) Insert commentary here, bullet points are fine > 

```{r req_2a}



```

## New variables created

Brief notes on why the variables created could be useful:

< (Delete this line) Insert commentary here, bullet points are fine >

```{r req_2b}



```

## Text data

```{r req_2c}



```

# Data-informed insights and recommendations

## Topics content creators have been posting about

< (Delete this line) Type insights here, bullet points are fine >

```{r req_3ai}
# Term frequency analysis


```

```{r req_3aii}
# Topic modelling


```

## Level of user engagement and factors that influence user engagement

< (Delete this line) Type insights and recommendations here, bullet points are fine >

```{r req_3b}



```
