---
title: "Individual Task 1 – Fonterra Social Media Analysis"
author: "Sheikh Mohammad Milton"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    df_print: paged
---

# 1. Introduction

## 1.1 Purpose of the analysis

This assignment analyses Fonterra's social media content to identify the main topics discussed across its official social media accounts and to examine user engagement with that content. The analysis uses the supplied `fonterra.csv` dataset and is completed in R.

The analysis focuses on two main questions:

1. What topics have content creators been posting about on Fonterra's social media accounts?
2. What is the level of user engagement, and what factors may influence engagement?

The analysis includes data preparation, term-frequency analysis, topic modelling, exploratory data analysis, bivariate statistical analysis, and data-informed recommendations.

## 1.2 Load packages

```{r initial}
# Install and load packages
if(!require("pacman"))install.packages("pacman")
pacman::p_load(readr, dplyr, tidyr, stringr, lubridate, purrr, ggplot2, gridExtra, GGally, corrplot)
pacman::p_load(tidytext, textstem, wordcloud, textdata, topicmodels)
pacman::p_load(DescTools, skimr, finalfit, rstatix, huxtable, jtools, knitr)

# Set random seed for reproducibility
set.seed(636)

```

# 2. Data Import and Initial Inspection

## 2.1 Import the dataset

```{r Import Data}
# Import and preview data
data_raw <- read_csv("fonterra.csv", locale = locale(encoding = "ISO-8859-1"), show_col_types = FALSE)

```

## 2.1 Initial Inspection

```{r Initial Inspection}
# Display the dimensions of the dataset
dim(data_raw)

# Inspect the variable names and data types
glimpse(data_raw)

# Display the first 10 rows
head(data_raw, 10)

# Display distinct values
unique(data_raw$platform)
unique(data_raw$media)

# Checking decimal value in count variables
data_raw |>
  summarise(across(where(is.numeric), ~ any(.x %% 1 != 0, na.rm = TRUE)))
```

## 2.2 Dataset overview

```{r dataset-overview}
# Create a compact overview of the dataset.
overview <- tibble(
  item = c("Number of observations", "Number of variables",
           "Number of platforms", "Number of unique URLs"),
  value = c(
    nrow(data_raw),
    ncol(data_raw),
    n_distinct(data_raw$platform),
    n_distinct(data_raw$url)
  )
)

kable(overview, caption = "Overview of the Fonterra dataset")

rm(overview)
```

```{r platform-counts}
# Count observations by social media platform
platform_counts <- data_raw |>
  count(platform, sort = TRUE)

kable(platform_counts, caption = "Number of observations by platform")

# Count observations by media
media_counts <- data_raw |>
  count(media, sort = TRUE)

kable(media_counts, caption = "Number of observations by media")

rm(platform_counts, media_counts)
```

## 2.3 Missing values

```{r missing-values}
# Count missing values in each variable.
missing_summary <- data_raw |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "missing_count"
  ) |>
  mutate(
    missing_percent = missing_count / nrow(data_raw) * 100
  ) |>
  arrange(desc(missing_count))

kable(
  missing_summary,
  digits = 2,
  caption = "Missing values by variable"
)

rm(missing_summary)
```

**Observation:**

i) Dataset under review has 9001 rows/ observations against 9 columns/ variables

ii) Data Type:

Character: platform, url, createdAt, text and media
Number: commentCount, shareCount, shareCount, likeCount and videoplayCount

iii) For better and accurate analysis, we must transform existing data type to their actual data format. We must transform:

a) platform and media to categorical data type
b) createdAt to DATE data type
c) commentCount, shareCount, likeCount and videoplayCount to INTEGER data type

iv) Maximum missing values exists in videoplayCount. This is natural since there may have several posts which don't have any video content

v) 6994 observations have no specified media and there exists naming difference in media. It shows video and Video in separte category although the main difference exist in first letter. Also Photo, Image and image are same type media. So, adjustment is required to align this ambiguities.

# 3. Data Preparation

## 3.1 Non-text data

### 3.1.1 Date and Time

The createdAt variable is converted to a date-time variable. Separate year, month and day-of-week variables are also created for later analysis.

```{r req_2a}
# Convert createdAt to a date-time variable and create useful time variables
data <- data_raw |>
  mutate(
    created_datetime = ymd_hms(createdAt, quiet = TRUE, tz = "UTC"),
    year = year(created_datetime),
    month = month(created_datetime, label = TRUE, abbr = TRUE),
    day_of_week = wday(created_datetime, label = TRUE, abbr = TRUE, week_start = 1)
  )

# Check maximum and minimum year and whether any dates failed to convert
print(min(year(data$created_datetime), na.rm = TRUE))
print(max(year(data$created_datetime), na.rm = TRUE))
sum(is.na(data$created_datetime))

```

**Observation:**

i) We have data/ observations  ranging from the year 2010 to 2026
ii) There exists no data failed to convert

### 3.1.2 Number Data

The commentCount, shareCount, likeCount and videoplayCount variables are converted to integer number

```{r}
# Converting commentCount, shareCount, likeCount and videoplayCount variables to integer number
data <- data |>
  mutate(across(
    c(commentCount, shareCount, likeCount, videoplayCount), 
    as.integer
  ))

# View data types and see if NA values are still present
summary(data[c("commentCount", "shareCount", "likeCount", "videoplayCount")])
```

## 3.2 CATEGORICAL data

### 3.2.1 Converting to CATEGORICAL data

```{r}
# Converting platform and media variables to categorical data type
data$platform <- as.factor(data$platform)
data$media <- as.factor(data$media)
```

### 3.2.2 Standardised media categories

The `media` variable contains inconsistent capitalisation such as `Video` and `video`, and `Image` and `image`. These values are standardised into consistent categories.

**Data-preparation judgement:** `Photo` and `Image` are treated as the same broad media category, and `Video` and `video` are treated as the same category because the difference is only capitalisation/ label wording. Missing media values are retained as `No media recorded` rather than assumed to represent a particular media format.

```{r media-preparation}
# Standardise media labels while retaining missing media information.
data <- data |>
  mutate(
    media_type = case_when(
      is.na(media) ~ "No media recorded",
      str_to_lower(media) %in% c("photo", "image") ~ "Image",
      str_to_lower(media) == "video" ~ "Video",
      str_to_lower(media) == "sidecar" ~ "Sidecar",
      TRUE ~ "Other"
    ),
    media_type = factor(
      media_type,
      levels = c("No media recorded", "Image", "Video", "Sidecar", "Other")
    )
  )

data |>
  count(media_type, sort = TRUE) |>
  kable(caption = "Standardised media categories")
```


## 3.3 Create new variables

### 3.3.1 Creating Social Engagement variable

**Judgement:** Missing comments and shares are not automatically interpreted as zero in the original variables. For the derived `social_engagement` measure, `coalesce()` is used so that the measure can be calculated, while the original missingness remains available for inspection. `videoplayCount` is not included in this combined measure because video plays are conceptually different from likes, comments and shares

```{r engagement-preparation}
# Missing values in commentCount, shareCount and likeCount variables are treated as zero which means no social interaction
# Create indicators and a social-engagement measure. Likes, comments and shares are treated as direct social interactions. Video plays are kept separate because they represent consumption rather than the same type of interaction
data <- data |>
  mutate(
    social_engagement =
      coalesce(likeCount, 0) +
      coalesce(commentCount, 0) +
      coalesce(shareCount, 0),
    has_video_plays = !is.na(videoplayCount) & videoplayCount > 0,
    has_media = media_type != "No media recorded"
  )

summary(data$social_engagement)
```

### 3.3.2 Text length and word count

**Judgement:** `text_length` and `word_count` can be used to investigate whether longer posts are associated with different engagement levels.

```{r text-variables}
# Create text-based variables that can be used to investigate whether content length is associated with user engagement.
data <- data |>
  mutate(
    text_clean_for_length = replace_na(text, ""),
    text_length = str_length(text_clean_for_length),
    word_count = str_count(
      str_squish(text_clean_for_length),
      "\\S+"
    )
  )

summary(data |> select(text_length, word_count))
```

### 3.3.3 Video-content indicator

**Judgement:** `media_type`, `has_media`, and `is_video` allow engagement to be compared across different content formats.

```{r video-indicator}
# Create a simple indicator for content that is explicitly identified as video.
data <- data %>%
  mutate(
    is_video = media_type == "Video"
  )

data %>%
  count(is_video) %>%
  mutate(percent = n / sum(n) * 100) %>%
  kable(digits = 2, caption = "Video and non-video observations")
```

## 3.4 Checking duplicate records

**Data-preparation judgement:** Duplicate records should not be removed automatically without checking their meaning. In this dataset, URLs are checked first because the URL is a useful content identifier. If duplicate observations are identified, their content and timestamps should be reviewed before deciding whether they represent repeated content or data errors.

```{r duplicates}
# Check for duplicated URLs and completely duplicated rows
duplicate_url_count <- sum(duplicated(data$url))
duplicate_row_count <- sum(duplicated(data))

tibble(
  duplicate_type = c("Duplicated URLs", "Duplicated complete rows"),
  count = c(duplicate_url_count, duplicate_row_count)
) %>%
  kable(caption = "Duplicate record checks")

rm(duplicate_url_count, duplicate_row_count)
```

```{r remove-exact-duplicates}
# Remove only completely duplicated rows.This is a conservative choice because identical URLs do not necessarily mean that the records are errors.
data <- data |>
  distinct()
```

# 4. Text Data Preparation

## 4.1 Prepare text for analysis

The `text` variable is prepared for term-frequency analysis and topic modelling. URLs, punctuation, numbers and common stop words are removed. The text is converted to lower case and tokenised into individual words.

```{r text-cleaning}
custom_stopwords <- tibble(
  word = c("https", "http", "www", "com",
           "fonterra", "nz", "new", "zealand"),
  lexicon = "custom"
)

stop_words <- bind_rows(stop_words, custom_stopwords)

clean_ngram <- function(data, n_size, col_name) {
  data |>
    unnest_tokens(!!sym(col_name), text, token = "ngrams", n = n_size) |>
    filter(
      str_detect(!!sym(col_name), paste0("^([a-z]+ ){", n_size - 1, "}[a-z]+$")),
      !str_detect(!!sym(col_name), "\\bhttps?\\b")
    ) |>
    filter(
      map_lgl(str_split(!!sym(col_name), " "), ~ !any(.x %in% stop_words$word))
    )
}

# Create a text dataset and remove missing/blank text.
text_data <- data |>
  select(url, platform, text) |>
  mutate(text = replace_na(text, "")) |>
  filter(str_squish(text) != "") |>
  mutate(document = row_number())

# Tokenise text into ngrams up to n = 1 to 6
uni_clean      <- clean_ngram(text_data, 1, "word")
bigram_clean   <- clean_ngram(text_data, 2, "bigram")
trigram_clean  <- clean_ngram(text_data, 3, "trigram")
quadgram_clean <- clean_ngram(text_data, 4, "quadgram")
pentagram_clean <- clean_ngram(text_data, 5, "pentagram")
hexagram_clean  <- clean_ngram(text_data, 6, "hexagram")

rm(clean_ngram, custom_stopwords, text_data, stop_words)

```

## 4.2 Observing most frequent words

```{r text-cleaning}
# Observing most frequent words
# Combine datasets and metadata into a structured list
ngram_list <- list(
  list(data = uni_clean, col = "word", name = "one word"),
  list(data = bigram_clean, col = "bigram", name = "two word"),
  list(data = trigram_clean, col = "trigram", name = "three word"),
  list(data = quadgram_clean, col = "quadgram", name = "four word"),
  list(data = pentagram_clean, col = "pentagram", name = "five word"),
  list(data = hexagram_clean, col = "hexagram", name = "six word")
)

# Generate all tables in a single operation
purrr::walk(ngram_list, function(ng) {
  ng$data |>
    count(!!sym(ng$col), sort = TRUE) |>
    slice_head(n = 30) |>
    kable(caption = paste("Initial most frequent", ng$name, "terms")) |>
    print()
})

```

## 4.3 Stemming and Lemmatisation
Depending on the data, stemming and lemmatisation has been performed to improve usability of the output, make no difference, or lead to incorrect conclusions if the meaning of the words diverts too much from their original meaning.

```{r}
# Unigram
## Stem and lemmatise words
uni_sl <- uni_clean |>
  mutate(uni_stem = stem_words(word),
         uni_lemma = lemmatize_words(word))

## Comparison of the original, stemmed, and lemmatised forms
g1 <- uni_sl |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g2 <- uni_sl |>
  count(uni_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(uni_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g3 <- uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(uni_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g1, g2, g3, ncol = 3)

## Keep lemmatised form and override object
uni_clean <- uni_sl |>
  select(-c(word, uni_stem)) |>
  rename(word = uni_lemma)

# Bigram
## Stem and lemmatise bigrams
bi_sl <- bigram_clean |>
  mutate(bigram_stem = stem_strings(bigram),
         bigram_lemma = lemmatize_strings(bigram))

## Comparison of the original, stemmed, and lemmatised forms
g4 <- bi_sl |>
  count(bigram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g5 <- bi_sl |>
  count(bigram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g6 <- bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g4, g5, g6, ncol = 3)

## Keep lemmatised form and override object
bi_clean <- bi_sl |>
  select(-c(bigram, starts_with("word"), contains("stem"))) |>
  rename(bigram = bigram_lemma)

# Trigram
## Stem and lemmatise Trigrams
tri_sl <- trigram_clean |>
  mutate(trigram_stem = stem_strings(trigram),
         trigram_lemma = lemmatize_strings(trigram))

## Comparison of the original, stemmed, and lemmatised forms
g7 <- tri_sl |>
  count(trigram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g8 <- tri_sl |>
  count(trigram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g9 <- tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g7, g8, g9, ncol = 3)

## Keep lemmatised form and override object
tri_clean <- tri_sl |>
  select(-c(trigram, starts_with("word"), contains("stem"))) |>
  rename(trigram = trigram_lemma)

# Quadgram
## Stem and lemmatise Quadgrams
quad_sl <- quadgram_clean |>
  mutate(quadgram_stem = stem_strings(quadgram),
         quadgram_lemma = lemmatize_strings(quadgram))

## Comparison of the original, stemmed, and lemmatised forms
g10 <- quad_sl |>
  count(quadgram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g11 <- quad_sl |>
  count(quadgram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g12 <- quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g10, g11, g12, ncol = 3)

## Keep lemmatised form and override object
quad_clean <- quad_sl |>
  select(-c(quadgram, starts_with("word"), contains("stem"))) |>
  rename(quadgram = quadgram_lemma)

# Pentagram
## Stem and lemmatise Fivegrams
penta_sl <- pentagram_clean |>
  mutate(pentagram_stem = stem_strings(pentagram),
         pentagram_lemma = lemmatize_strings(pentagram))

## Comparison of the original, stemmed, and lemmatised forms
g13 <- penta_sl |>
  count(pentagram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g14 <- penta_sl |>
  count(pentagram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g15 <- penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g13, g14, g15, ncol = 3)

## Keep lemmatised form and override object
penta_clean <- penta_sl |>
  select(-c(pentagram, starts_with("word"), contains("stem"))) |>
  rename(pentagram = pentagram_lemma)

# Sixgram
## Stem and lemmatise Sixgrams
hexa_sl <- hexagram_clean |>
  mutate(hexagram_stem = stem_strings(hexagram),
         hexagram_lemma = lemmatize_strings(hexagram))

## Comparison of the original, stemmed, and lemmatised forms
g16 <- hexa_sl |>
  count(hexagram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g17 <- hexa_sl |>
  count(hexagram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g18 <- hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g16, g17, g18, ncol = 3)

## Keep lemmatised form and override object
hexa_clean <- hexa_sl |>
  select(-c(hexagram, starts_with("word"), contains("stem"))) |>
  rename(hexagram = hexagram_lemma)


rm(g1, g2, g3, g4, g5, g6, g7, g8, g9, g10, g11, g12, g13, g14, g15, g16, g17, g18, uni_clean, bi_clean, ngram_list, bigram_clean, tri_clean, trigram_clean, quad_clean, quadgram_clean, five_clean, fivegram_clean, six_clean, sixgram_clean)

```

# 5. What Topics Have Content Creators Been Posting About?

## 5.1 Term Frequency Analysis

```{r term-frequency}
# Calculate term frequencies.
# Unigram
## Word count table
uni_sl |>
  count(lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
uni_sl |>
  count(lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(lemma, n))) +
  geom_col(fill = "deepskyblue") +
  labs(title = "Top 20 Unigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
uni_sl |>
  group_by(lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Bigram
## Word count table
bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(bigram_lemma, n))) +
  geom_col(fill = "deepskyblue") +
  labs(title = "Top 20 Bigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
bi_sl |>
  group_by(bigram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = bigram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))
# Trigram
## Word count table
tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(trigram_lemma, n))) +
  geom_col(fill = "deepskyblue") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
tri_sl |>
  group_by(trigram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = trigram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))
