---
title: "Individual Task 1 – Fonterra Social Media Analysis"
author: "Sheikh Mohammad Milton, ID No. 1713714"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    df_print: paged
  pdf_document:
    toc: true
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

# 1. Introduction

## 1.1 Purpose of the analysis

This assignment analyses Fonterra's social media content to identify the main topics discussed across its official social media accounts and to examine user engagement with that content. The analysis uses the supplied `fonterra.csv` dataset and is completed in R.

The analysis includes data preparation, term-frequency analysis, topic modelling, exploratory data analysis, bivariate statistical analysis, and data-informed recommendations.

## 1.2 Load packages

```{r initial}
# Install and load packages
if(!require("pacman"))install.packages("pacman")
pacman::p_load(readr, dplyr, tidyr, stringr, lubridate, purrr, ggplot2, gridExtra, GGally, corrplot)
pacman::p_load(tidytext, textstem, wordcloud, textdata, topicmodels)
pacman::p_load(DescTools, skimr, finalfit, rstatix, huxtable, jtools)
pacman::p_load(knitr, easystats, gtsummary, gt, scales)

```

# 2. Data Import and Initial Inspection

## 2.1 Import the dataset

```{r Import Data}
# Import and preview data
data_raw <- read_csv("fonterra.csv", show_col_types = FALSE)

```

## 2.1 Initial Inspection

```{r Initial Inspection}
# Display the dimensions of the dataset
dim(data_raw)

# Inspect the variable names and data types
glimpse(data_raw)

# Display the first 10 rows
head(data_raw, 10)

# Display distinct values
unique(data_raw$platform)
unique(data_raw$media)

# Checking decimal value in count variables
data_raw |>
  summarise(across(where(is.numeric), ~ any(.x %% 1 != 0, na.rm = TRUE)))
```

## 2.2 Dataset overview

```{r dataset-overview}
# Create a compact overview of the dataset.
overview <- tibble(
  item = c("Number of observations", "Number of variables",
           "Number of platforms", "Number of unique URLs"),
  value = c(
    nrow(data_raw),
    ncol(data_raw),
    n_distinct(data_raw$platform),
    n_distinct(data_raw$url)
  )
)

kable(overview, caption = "Overview of the Fonterra dataset")

rm(overview)
```

```{r platform-counts}
# Count observations by social media platform
platform_counts <- data_raw |>
  count(platform, sort = TRUE)

kable(platform_counts, caption = "Number of observations by platform")

# Count observations by media
media_counts <- data_raw |>
  count(media, sort = TRUE)

kable(media_counts, caption = "Number of observations by media")

rm(platform_counts, media_counts)
```

## 2.3 Missing values

```{r missing-values}
# Count missing values in each variable.
missing_summary <- data_raw |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "missing_count"
  ) |>
  mutate(
    missing_percent = missing_count / nrow(data_raw) * 100
  ) |>
  arrange(desc(missing_count))

kable(
  missing_summary,
  digits = 2,
  caption = "Missing values by variable"
)

rm(missing_summary)
```

**Observation:**

i) Dataset under review has 9001 rows/ observations against 9 columns/ variables

ii) Data Type:

Character: platform, url, createdAt, text and media
Number: commentCount, shareCount, shareCount, likeCount and videoplayCount

iii) For better and accurate analysis, we must transform existing data type to their actual data format. We must transform:

a) platform and media to categorical data type
b) createdAt to DATE data type
c) commentCount, shareCount, likeCount and videoplayCount to INTEGER data type

iv) Maximum missing values exists in videoplayCount. This is natural since there may have several posts which don't have any video content

v) 6994 observations have no specified media and there exists naming difference in media. It shows video and Video in separte category although the main difference exist in first letter. Also Photo, Image and image are same type media. So, adjustment is required to align this ambiguities.

# 3. Data Preparation

## 3.1 Non-text data

### 3.1.1 Date and Time

The createdAt variable is converted to a date-time variable. Separate year, month and day-of-week variables are also created for later analysis.

```{r req_2a}
# Convert createdAt to a date-time variable and create useful time variables
data <- data_raw |>
  mutate(
    created_datetime = ymd_hms(createdAt, quiet = TRUE, tz = "UTC"),
    year = year(created_datetime),
    month = month(created_datetime, label = TRUE, abbr = TRUE),
    day_of_week = wday(created_datetime, label = TRUE, abbr = TRUE, week_start = 1)
  )

# Check maximum and minimum year and whether any dates failed to convert
print(min(year(data$created_datetime), na.rm = TRUE))
print(max(year(data$created_datetime), na.rm = TRUE))
sum(is.na(data$created_datetime))

```

**Observation:**

i) We have data/ observations  ranging from the year 2010 to 2026
ii) There exists no data failed to convert

### 3.1.2 Number Data

The commentCount, shareCount, likeCount and videoplayCount variables are converted to integer number

```{r}
# Converting commentCount, shareCount, likeCount and videoplayCount variables to integer number
data <- data |>
  mutate(across(
    c(commentCount, shareCount, likeCount, videoplayCount), 
    as.integer
  ))

# View data types and see if NA values are still present
summary(data[c("commentCount", "shareCount", "likeCount", "videoplayCount")])
```

## 3.2 CATEGORICAL data

### 3.2.1 Converting to CATEGORICAL data

```{r}
# Converting platform and media variables to categorical data type
data$platform <- as.factor(data$platform)
data$media <- as.factor(data$media)
```

### 3.2.2 Standardised media categories

The `media` variable contains inconsistent capitalisation such as `Video` and `video`, and `Image` and `image`. These values are standardised into consistent categories.

**Data-preparation judgement:** `Photo` and `Image` are treated as the same broad media category, and `Video` and `video` are treated as the same category because the difference is only capitalisation/ label wording. Missing media values are retained as `No media recorded` rather than assumed to represent a particular media format.

```{r media-preparation}
# Standardise media labels while retaining missing media information.
data <- data |>
  mutate(
    media_type = case_when(
      is.na(media) ~ "No media recorded",
      str_to_lower(media) %in% c("photo", "image") ~ "Image",
      str_to_lower(media) == "video" ~ "Video",
      str_to_lower(media) == "sidecar" ~ "Sidecar",
      TRUE ~ "Other"
    ),
    media_type = factor(
      media_type,
      levels = c("No media recorded", "Image", "Video", "Sidecar", "Other")
    )
  )

data |>
  count(media_type, sort = TRUE) |>
  kable(caption = "Standardised media categories")
```


## 3.3 Create new variables

### 3.3.1 Creating Social Engagement variable

**Judgement:** In the original data, missing comments and shares are left as missing. They are not changed to zero, because a missing value often means the platform did not report that number. For example, shares are missing for all Instagram and YouTube posts. To calculate social_engagement (likes + comments + shares), I treated missing comments and shares as zero, using coalesce(). This means the measure is a minimum value and may be too low for platforms that do not report shares. likeCount has no missing values, so it is the most reliable measure across platforms. I did not include videoplayCount because it counts views, not interactions such as likes, comments and shares

```{r engagement-preparation}
# Missing comments and shares are treated as zero only to calculate the total.

# The original columns keep their missing values, because missing often means "not reported".

# Create indicators and a social-engagement measure. Likes, comments and shares are treated as direct social interactions. Video plays are kept separate because they represent consumption rather than the same type of interaction

data <- data |>
  mutate(
    social_engagement =
      coalesce(likeCount, 0) +
      coalesce(commentCount, 0) +
      coalesce(shareCount, 0),
    has_video_plays = !is.na(videoplayCount) & videoplayCount > 0,
    has_media = media_type != "No media recorded"
  )

summary(data$social_engagement)
```

### 3.3.2 Text length and word count

**Judgement:** `text_length` and `word_count` can be used to investigate whether longer posts are associated with different engagement levels.

```{r text-variables}
data <- data |>
  mutate(
    text_clean_for_length = replace_na(text, ""),
    text_length = str_length(text_clean_for_length),
    word_count = str_count(
      str_squish(text_clean_for_length),
      "\\S+"
    )
  )

summary(data |> select(text_length, word_count))
```

### 3.3.3 Video-content indicator

**Judgement:** `media_type`, `has_media`, and `is_video` allow engagement to be compared across different content formats.

```{r video-indicator}
# Create a simple indicator for content that is explicitly identified as video.
data <- data |>
  mutate(
    is_video = media_type == "Video"
  )

data |>
  count(is_video) |>
  mutate(percent = n/sum(n) * 100) |>
  kable(digits = 2, caption = "Video and non-video observations")
```

## 3.4 Checking duplicate records

**Data-preparation judgement:** Duplicate records should not be removed automatically without checking their meaning. In this dataset, URLs are checked first because the URL is a useful content identifier. If duplicate observations are identified, their content and timestamps should be reviewed before deciding whether they represent repeated content or data errors.

```{r duplicates}
# Check for duplicated URLs and completely duplicated rows
duplicate_url_count <- sum(duplicated(data$url))
duplicate_row_count <- sum(duplicated(data))

tibble(
  duplicate_type = c("Duplicated URLs", "Duplicated complete rows"),
  count = c(duplicate_url_count, duplicate_row_count)
) |>
  kable(caption = "Duplicate record checks")

rm(duplicate_url_count, duplicate_row_count)
```


```{r remove-exact-duplicates}
# Remove only completely duplicated rows.This is a conservative choice because identical URLs do not necessarily mean that the records are errors.
data <- data |>
  distinct()
```

** No duplicate records found **

# 4. Text Data Preparation

## 4.1 Prepare text for analysis

The `text` variable is prepared for term-frequency analysis and topic modelling. URLs, punctuation, numbers and common stop words are removed. The text is converted to lower case and tokenised into individual words.

```{r text-cleaning}
custom_stopwords <- tibble(
     word = c("https", "http", "www", "com", "fonterra", "nz", "new", "zealand", "amp", "uh", "um", "hey", "yeah", "okay", "gonna"),
     lexicon = "custom"
     )

stop_words <- bind_rows(stop_words, custom_stopwords)

clean_ngram <- function(data, n_size, col_name) {
  data |>
    unnest_tokens(!!sym(col_name), text, token = "ngrams", n = n_size) |>
    filter(
      str_detect(!!sym(col_name), paste0("^([a-z]+ ){", n_size - 1, "}[a-z]+$")),
      !str_detect(!!sym(col_name), "\\bhttps?\\b")
    ) |>
    filter(
      map_lgl(str_split(!!sym(col_name), " "), ~ !any(.x %in% stop_words$word))
    )
}

# Create a text dataset and remove missing/blank text.
text_data <- data |>
  select(url, platform, text) |>
  mutate(text = replace_na(text, "")) |>
  filter(str_squish(text) != "") |>
  mutate(document = row_number())

# Tokenise text into ngrams up to n = 1 to 6
uni_clean      <- clean_ngram(text_data, 1, "word")
bigram_clean   <- clean_ngram(text_data, 2, "bigram")
trigram_clean  <- clean_ngram(text_data, 3, "trigram")
quadgram_clean <- clean_ngram(text_data, 4, "quadgram")
pentagram_clean <- clean_ngram(text_data, 5, "pentagram")
hexagram_clean  <- clean_ngram(text_data, 6, "hexagram")

uni_clean <- uni_clean |> filter(nchar(word) > 2)

rm(clean_ngram, custom_stopwords, text_data, stop_words)

```

## 4.2 Observing most frequent words

```{r frequent-words}
# Observing most frequent words
# Combine datasets and metadata into a structured list
ngram_list <- list(
  list(data = uni_clean, col = "word", name = "one word"),
  list(data = bigram_clean, col = "bigram", name = "two word"),
  list(data = trigram_clean, col = "trigram", name = "three word"),
  list(data = quadgram_clean, col = "quadgram", name = "four word"),
  list(data = pentagram_clean, col = "pentagram", name = "five word"),
  list(data = hexagram_clean, col = "hexagram", name = "six word")
)

# Generate all tables in a single operation
purrr::walk(ngram_list, function(ng) {
  ng$data |>
    count(!!sym(ng$col), sort = TRUE) |>
    slice_head(n = 30) |>
    kable(caption = paste("Initial most frequent", ng$name, "terms")) |>
    print()
})

```

## 4.3 Stemming and Lemmatisation
Depending on the data, stemming and lemmatisation has been performed to improve usability of the output, make no difference, or lead to incorrect conclusions if the meaning of the words diverts too much from their original meaning.

```{r}
# Unigram
## Stem and lemmatise words
uni_sl <- uni_clean |>
  mutate(uni_stem = stem_words(word),
         uni_lemma = lemmatize_words(word))

## Comparison of the original, stemmed, and lemmatised forms
g1 <- uni_sl |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(word, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g2 <- uni_sl |>
  count(uni_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(uni_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g3 <- uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(uni_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g1, g2, g3, ncol = 3)

## Keep lemmatised form and override object
uni_clean <- uni_sl |>
  select(-c(word, uni_stem)) |>
  rename(word = uni_lemma)

# Bigram
## Stem and lemmatise bigrams
bi_sl <- bigram_clean |>
  mutate(bigram_stem = stem_strings(bigram),
         bigram_lemma = lemmatize_strings(bigram))

## Comparison of the original, stemmed, and lemmatised forms
g4 <- bi_sl |>
  count(bigram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g5 <- bi_sl |>
  count(bigram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g6 <- bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(bigram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g4, g5, g6, ncol = 3)

## Keep lemmatised form and override object
bi_clean <- bi_sl |>
  select(-c(bigram, starts_with("word"), contains("stem"))) |>
  rename(bigram = bigram_lemma)

# Trigram
## Stem and lemmatise Trigrams
tri_sl <- trigram_clean |>
  mutate(trigram_stem = stem_strings(trigram),
         trigram_lemma = lemmatize_strings(trigram))

## Comparison of the original, stemmed, and lemmatised forms
g7 <- tri_sl |>
  count(trigram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g8 <- tri_sl |>
  count(trigram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g9 <- tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(trigram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g7, g8, g9, ncol = 3)

## Keep lemmatised form and override object
tri_clean <- tri_sl |>
  select(-c(trigram, starts_with("word"), contains("stem"))) |>
  rename(trigram = trigram_lemma)

# Quadgram
## Stem and lemmatise Quadgrams
quad_sl <- quadgram_clean |>
  mutate(quadgram_stem = stem_strings(quadgram),
         quadgram_lemma = lemmatize_strings(quadgram))

## Comparison of the original, stemmed, and lemmatised forms
g10 <- quad_sl |>
  count(quadgram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g11 <- quad_sl |>
  count(quadgram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g12 <- quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(quadgram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g10, g11, g12, ncol = 3)

## Keep lemmatised form and override object
quad_clean <- quad_sl |>
  select(-c(quadgram, starts_with("word"), contains("stem"))) |>
  rename(quadgram = quadgram_lemma)

# Pentagram
## Stem and lemmatise Fivegrams
penta_sl <- pentagram_clean |>
  mutate(pentagram_stem = stem_strings(pentagram),
         pentagram_lemma = lemmatize_strings(pentagram))

## Comparison of the original, stemmed, and lemmatised forms
g13 <- penta_sl |>
  count(pentagram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g14 <- penta_sl |>
  count(pentagram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g15 <- penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(pentagram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g13, g14, g15, ncol = 3)

## Keep lemmatised form and override object
penta_clean <- penta_sl |>
  select(-c(pentagram, starts_with("word"), contains("stem"))) |>
  rename(pentagram = pentagram_lemma)

# Hexagram
## Stem and lemmatise Sixgrams
hexa_sl <- hexagram_clean |>
  mutate(hexagram_stem = stem_strings(hexagram),
         hexagram_lemma = lemmatize_strings(hexagram))

## Comparison of the original, stemmed, and lemmatised forms
g16 <- hexa_sl |>
  count(hexagram, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram, n))) +
  geom_col() +
  labs(title = "Original", x = NULL, y = NULL)

g17 <- hexa_sl |>
  count(hexagram_stem, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram_stem, n))) +
  geom_col() +
  labs(title = "Stemming", x = NULL, y = NULL)

g18 <- hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(order_by = n, n = 20) |>
  ggplot(aes(x = n, y = reorder(hexagram_lemma, n))) +
  geom_col() +
  labs(title = "Lemmatising", x = NULL, y = NULL)

grid.arrange(g16, g17, g18, ncol = 3)

## Keep lemmatised form and override object
hexa_clean <- hexa_sl |>
  select(-c(hexagram, starts_with("word"), contains("stem"))) |>
  rename(hexagram = hexagram_lemma)


rm(g1, g2, g3, g4, g5, g6, g7, g8, g9, g10, g11, g12, g13, g14, g15, g16, g17, g18, bi_clean, ngram_list, bigram_clean, tri_clean, trigram_clean, quad_clean, quadgram_clean, penta_clean, pentagram_clean, hexa_clean, hexagram_clean)

```

# 5. What Topics Have Content Creators Been Posting About?

## 5.1 Term Frequency Analysis

```{r}
# Calculate term frequencies.
# Unigram
## Word count table
uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
uni_sl |>
  count(uni_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(uni_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Unigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
uni_sl |>
  group_by(uni_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = uni_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Bigram
## Word count table
bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
bi_sl |>
  count(bigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(bigram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Bigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
bi_sl |>
  group_by(bigram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = bigram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))
# Trigram
## Word count table
tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
tri_sl |>
  count(trigram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(trigram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
tri_sl |>
  group_by(trigram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = trigram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Quadgram
## Word count table
quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
quad_sl |>
  count(quadgram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(quadgram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
quad_sl |>
  group_by(quadgram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = quadgram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Pentagram
## Word count table
penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
penta_sl |>
  count(pentagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(pentagram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
penta_sl |>
  group_by(pentagram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = pentagram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))

# Hexagram
## Word count table
hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n)

## Ordered bar chart
hexa_sl |>
  count(hexagram_lemma, sort = TRUE) |>
  slice_max(n = 20, order_by = n) |>
  ggplot(aes(x = n, y = reorder(hexagram_lemma, n))) +
  geom_col(fill = "royalblue3") +
  labs(title = "Top 20 Trigrams",  x = NULL,  y = NULL) +
  theme_minimal()

## Wordcloud
hexa_sl |>
  group_by(hexagram_lemma) |>
  summarise(count = n()) |>
  with(wordcloud(words = hexagram_lemma, 
                 freq = count, 
                 max.words = 100,
                 rot.per = 0.2,
                 random.order = FALSE, 
                 colors = brewer.pal(8, "Dark2"),
                 scale = c(1.5, 0.5)
                 ))
```

## 5.2 Topic Modelling

A Latent Dirichlet Allocation (LDA) model with six topics is fitted as an initial model, following the assignment guidance.

```{r topic-modelling-data}
# Prepare a document-term matrix for topic modelling.
# Documents with no remaining tokens are excluded from the model.
document_terms <- uni_clean |>
  count(document, word, sort = FALSE)

documents_with_tokens <- document_terms |>
  distinct(document)

dtm <- document_terms |>
  cast_dtm(document, word, n)

dim(dtm)
```

```{r lda-model}
# Fit an LDA model with six topics.
set.seed(1234)

lda_model <- LDA(
  dtm,
  k = 6,
  control = list(seed = 1234)
)

lda_model
```

## 5.3 Most probable words for each topic

```{r topic-words}
# Extract word probabilities for each topic.
topic_terms <- tidy(lda_model, matrix = "beta")

# Display the ten highest-probability words for each topic.
top_topic_words <- topic_terms |>
  group_by(topic) |>
  slice_max(beta, n = 10, with_ties = FALSE) |>
  arrange(topic, desc(beta))|>
  ungroup()

kable(
  top_topic_words,
  digits = 4,
  caption = "Top ten words by probability for each topic"
)
```

```{r topic-word-plot, fig.width=9, fig.height=8}
# Visualise the most probable words for each topic.
top_topic_words |>
  mutate(
    plot_term = reorder_within(term, beta, topic)
  ) |>
  ggplot(aes(x = plot_term, y = beta)) +
  geom_col() +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered() +
  labs(
    title = "Most Probable Words Within Each Topic",
    x = NULL,
    y = "Word Probability"
  ) +
  theme_minimal()
```

```{r topic-assignment}
# Assign each document its most probable topic (highest gamma) and join back to the main dataset
doc_topics <- tidy(lda_model, matrix = "gamma") |>
  group_by(document) |>
  slice_max(gamma, n = 1, with_ties = FALSE) |>
  ungroup() |>
  mutate(document = as.integer(document)) |>
  rename(topic_gamma = gamma)

# Topic labels: check these against YOUR top-words plot before using them
topic_labels <- tibble(
  topic = 1:6,
  topic_label = c("1 Farming & water", "2 Milk price & business", "3 Brand & World Milk Day",
                  "4 Community & awards", "5 Production & food", "6 Consumer products")
)

# Map document numbers back to post URLs, then join onto the main dataset
doc_url <- uni_clean |> distinct(document, url)

doc_topics <- doc_topics |>
  left_join(doc_url, by = "document") |>
  left_join(topic_labels, by = "topic") |>
  select(url, topic, topic_label, topic_gamma)

data <- data |> left_join(doc_topics, by = "url")

# Check: posts without a topic are those with no text or no tokens left after cleaning
data |> summarise(with_topic = sum(!is.na(topic)), without_topic = sum(is.na(topic)))
```

```{r topic-summary}
# Topic prevalence, topic mix by platform, and engagement by topic
topic_data <- data |> filter(!is.na(topic_label))

# Share of posts by topic
topic_data |> count(topic_label) |> mutate(percent = round(n / sum(n) * 100, 1)) |>
  kable(caption = "Share of posts by most probable topic")

# Topic mix within each platform
topic_data |>
  count(platform, topic_label) |>
  group_by(platform) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = platform, y = pct, fill = topic_label)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Topic mix by platform", x = NULL, y = "Share of posts", fill = "Topic") +
  theme_minimal()

# Median engagement by topic (topics are partly confounded with platform)
topic_data |>
  group_by(topic_label) |>
  summarise(posts = n(), median_engagement = median(social_engagement),
            mean_engagement = round(mean(social_engagement), 1), .groups = "drop") |>
  arrange(desc(median_engagement)) |>
  kable(caption = "Engagement by topic")

# Does engagement differ by topic? (Kruskal-Wallis + effect size)
topic_data |> kruskal_test(social_engagement ~ topic_label)
topic_data |> kruskal_effsize(social_engagement ~ topic_label)
```

**Commentary: what the term-frequency and topic results mean for Fonterra Insights:**

Topic 1: water, farm(er), people, product(s) — farming/sustainability themed

Topic 2: milk, farmer, business, million, china — financial/milk-price themed

Topic 3: team, milk, cheese, worldmilkday — brand/team themed

Topic 4: team, company, award, day, kid(s) — community/awards themed

Topic 5: milk, farm, product, food — production themed

Topic 6: cheese, cream, dairy, share, award — consumer product themed

**Discussion:** Fonterra's content is mostly about its core dairy business. The most frequent words are milk, farmer, dairy, farm and team. The most common two-word phrases are milk price, media release, farm source, dairy industry and farmgate milk. The most common three-word phrases are farmgate milk price, forecast farmgate milk, dairy industry award, grass root fund and world milk day. This shows that the accounts mainly talk about milk prices, farmers and communities, and industry news.

The topic model found six main themes. These are farming and water (Topic 1), milk price and business (Topic 2), brand and World Milk Day (Topic 3), community and awards (Topic 4), production and food (Topic 5) and consumer products (Topic 6). The biggest topic is [topic name, x% of posts] and the smallest is [topic name, y% of posts]. The themes match the phrases above, for example milk price (Topic 2), World Milk Day (Topic 3) and the dairy industry awards (Topic 4).

Each platform uses different content. TikTok is mostly about consumer brands (the top words are Anlene, Anmum and Anchor). Instagram posts often point to a link in the bio and feature content such as tanker drivers and the living water programme. LinkedIn has more about awards, support and food. X and Facebook cover a wide mix, and X has many thank-you replies.

Some topics get more engagement than others. As a simple check, posts that mention World Milk Day had a median engagement of about 27, compared with 5 for all posts, while posts about milk price had about 6. Because topics are partly linked to platform, and platform explains a lot of engagement, these differences are only suggestive.

**Recommendations:** 
1. Match topics to the platforms where they already do well, instead of posting every theme everywhere.

2. Give more space to topics and campaigns with high engagement, such as World Milk Day, and review topics that take up many posts but get little response.

3. Report topic shares and engagement by topic regularly, so the team can see which content works.

**Limitations of the topic model:** I used k = 6 and did not test other numbers of topics. Some words (for example milk, farm and team) appear in more than one topic, so the labels are my own interpretation. Short posts, such as replies on X, have little topic information, and YouTube captions contain spoken filler words that can affect the word counts. Removing very common dairy words, or trying a different k, could give clearer topics.

```{r}
# Keep only transformed 'data' object
rm(list = setdiff(ls(), "data"))
```

# 6. User Engagement Analysis

## 6.1 Exploratory data analysis

```{r}
# Data preparation

fonterra <- data |>
  mutate(
    platform  = factor(platform),
    media_type  = factor(media_type,
                         levels = c("No media recorded", "Image", "Sidecar", "Video")),
    day_of_week = factor(day_of_week,
                         levels = c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")),
    month = factor(month, levels = month.abb),

# Extra analysis variables
log_engagement = log1p(social_engagement),
engagement_level = factor(
  if_else(social_engagement > median(social_engagement),
          "High", "Low"),
  levels = c("Low", "High")),

media_present = factor(
  has_media, levels = c(FALSE, TRUE),
  labels = c("No media", "Has media")),

video_post    = factor(
  is_video, levels = c(FALSE, TRUE),
  labels = c("Not video", "Video")),

day_type  = factor(
  if_else(day_of_week %in% c("Sat","Sun"), "Weekend", "Weekday"),
  levels = c("Weekday", "Weekend")),

# Replies on X start with an @mention (customer-service style replies)

is_reply = factor(
  str_detect(coalesce(text, ""), "^@"),
  levels = c(FALSE, TRUE), 
  labels = c("Original post", "Reply"))
  )

glimpse(fonterra)

```

### 6.1.1 Descriptive statistics

```{r}
fonterra |>
  select(commentCount, shareCount, likeCount, videoplayCount, social_engagement, text_length, word_count) |>
  tbl_summary(
    type = all_continuous() ~ "continuous2",
    statistic = all_continuous() ~ c("{mean} ({sd})",
                                     "{median} ({p25}, {p75})",
                                     "{min}, {max}"),
    missing_text = "Missing"
  ) |>
  bold_labels()

```

```{r desc-by-platform}
fonterra |>
  select(platform, social_engagement, likeCount, commentCount, shareCount, text_length, media_type, day_type) |>
  tbl_summary(
    by = platform,
    statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", all_categorical() ~ "{n} ({p}%)"),
    missing = "no"
  ) |>
  add_overall() |>
  bold_labels()
```

```{r zero-engagement}
tibble(
  `Posts with zero engagement` =
    percent(mean(fonterra$social_engagement == 0), 0.1),
  `Skewness of engagement`  =
    round(datawizard::skewness(fonterra$social_engagement)$Skewness, 1),
  `Mean`   = round(mean(fonterra$social_engagement), 1),
  `Median` = median(fonterra$social_engagement))|>
  gt()
```

### 6.1.3 Distribution of engagement

```{r dist-engagement}
p1 <- ggplot(fonterra, aes(social_engagement)) +
  geom_histogram(bins = 60, fill = "#2a6f97") +
  labs(title = "Raw engagement (heavily right-skewed)", x = "Engagement", y = "Posts") +
  theme_modern()

p2 <- ggplot(fonterra, aes(log_engagement)) +
  geom_histogram(bins = 40, fill = "#61a5c2") +
  labs(title = "log(1 + engagement)", x = "log(1 + engagement)", y = "Posts") +
  theme_modern()

grid.arrange(p1, p2, ncol = 2)

```

```{r components}
fonterra |>
  summarise(Likes = sum(likeCount, na.rm = TRUE),
            Comments = sum(commentCount, na.rm = TRUE),
            Shares = sum(shareCount, na.rm = TRUE)) |>
  pivot_longer(everything(), names_to = "type", values_to = "total") |>
  mutate(share = total / sum(total)) |>
  ggplot(aes(reorder(type, share), share)) +
  geom_col(fill = "#2a6f97") +
  geom_text(aes(label = percent(share, 1)), hjust = -0.1) +
  coord_flip() +
  scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Composition of total engagement", x = NULL, y = NULL) +
  theme_modern()
```

### 6.1.4 Platform: volume versus engagement

```{r platform-share}
platform_summary <- fonterra |>
  group_by(platform) |>
  summarise(posts = n(),
            total_eng = sum(social_engagement),
            mean_eng = mean(social_engagement),
            median_eng = median(social_engagement),
            .groups = "drop") |>
  mutate(share_posts = posts / sum(posts),
         share_eng   = total_eng / sum(total_eng))

platform_summary |>
  arrange(desc(median_eng)) |>
  gt() |>
  fmt_number(c(mean_eng, median_eng), decimals = 1) |>
  fmt_percent(c(share_posts, share_eng), decimals = 1) |>
  tab_header(title = "Platform summary")

platform_summary |>
  select(platform, `Share of posts` = share_posts, `Share of engagement` = share_eng) |>
  pivot_longer(-platform) |>
  ggplot(aes(platform, value, fill = name)) +
  geom_col(position = "dodge") +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = c("#e07a5f", "#2a6f97")) +
  labs(title = "Share of posts vs share of engagement", x = NULL, y = NULL, fill = NULL) +
  theme_modern()
```


```{r platform-box}
ggplot(fonterra, aes(reorder(platform, social_engagement, median),
                     social_engagement + 1, fill = platform)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.2) +
  scale_y_log10(labels = comma) +
  coord_flip() +
  labs(title = "Engagement by platform (log scale)", x = NULL, y = "Engagement + 1") +
  theme_modern()
```

### 6.1.5 Content factors: media, text length

```{r media-plots}
ggplot(fonterra, aes(media_type, social_engagement + 1, fill = media_type)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.2) +
  scale_y_log10(labels = comma) +
  labs(title = "Engagement by media type (log scale)", x = NULL, y = "Engagement + 1") +
  theme_modern()

# Media type is confounded with platform: cross-tabulate
fonterra |>
  tbl_cross(row = platform, col = media_type, percent = "row")

# Same comparison within the platforms where media varies
fonterra |>
  filter(platform %in% c("Facebook", "LinkedIn", "Instagram")) |>
  ggplot(aes(media_type, social_engagement + 1, fill = media_type)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.2) +
  scale_y_log10(labels = comma) +
  facet_wrap(~ platform) +
  labs(title = "Media type within platform", x = NULL, y = "Engagement + 1") +
  theme_modern() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r engagement vs text-length}
ggplot(fonterra, aes(text_length + 1, social_engagement + 1)) +
  geom_point(alpha = 0.15, colour = "#2a6f97") +
  geom_smooth(method = "gam", colour = "#e07a5f") +
  scale_x_log10(labels = comma) + scale_y_log10(labels = comma) +
  labs(title = "Engagement vs text length (log-log)",
       x = "Text length (characters) + 1", y = "Engagement + 1") +
  theme_modern()

fonterra |>
  group_by(platform) |>
  summarise(median_text_length = median(text_length),
            max_text_length = max(text_length)) |>
  gt()
```

### 6.1.6 Time factors

```{r time-year}
fonterra |>
  group_by(year) |>
  summarise(posts = n(), median = median(social_engagement),
            mean = mean(social_engagement)) |>
  pivot_longer(c(median, mean)) |>
  ggplot(aes(year, value, colour = name)) +
  geom_line(linewidth = 1) + geom_point() +
  scale_colour_manual(values = c("#e07a5f", "#2a6f97")) +
  labs(title = "Engagement by year", x = NULL, y = "Engagement", colour = NULL) +
  theme_modern()

# Platform mix changes over time (important confounder)
fonterra |>
  count(year, platform) |>
  ggplot(aes(year, n, fill = platform)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = percent) +
  labs(title = "Platform mix by year", x = NULL, y = "Share of posts", fill = NULL) +
  theme_modern()
```

```{r time-dow-month}
p_dow <- fonterra |>
  group_by(day_of_week) |>
  summarise(median = median(social_engagement), n = n()) |>
  ggplot(aes(day_of_week, median)) +
  geom_col(fill = "#2a6f97") +
  labs(title = "Median engagement by weekday", x = NULL, y = "Median") +
  theme_modern()

p_mon <- fonterra |>
  group_by(month) |>
  summarise(median = median(social_engagement)) |>
  ggplot(aes(month, median)) +
  geom_col(fill = "#61a5c2") +
  labs(title = "Median engagement by month", x = NULL, y = "Median") +
  theme_modern()

grid.arrange(p_mon, p_dow, ncol = 2)
```

```{r video-plays}
fonterra |>
  filter(!is.na(videoplayCount)) |>
  ggplot(aes(videoplayCount, social_engagement + 1)) +
  geom_point(alpha = 0.3, colour = "#2a6f97") +
  geom_smooth(method = "lm", colour = "#e07a5f") +
  scale_x_log10(labels = comma) + scale_y_log10(labels = comma) +
  labs(title = "Engagement vs video plays (posts with play counts)",
       x = "Video plays", y = "Engagement + 1") +
  theme_modern()

rm(p1, p2, p_dow, p_mon, platform_summary)
```

## 6.2 Findings

**Level of engagement.** Engagement is very unevenly distributed. Across 9,001 posts the mean is about 60 interactions but the median is only 5, with about 16% of posts receiving no engagement at all and a maximum of 11,819. The distribution is extremely right-skewed (skewness about 19), so a small number of viral posts pull the mean far above a typical post. Medians and log-transformed values are therefore the honest summary. Likes make up the large majority of interactions; comments and shares are much rarer.

**Platform.** Twitter/X supplies about 69% of posts but only about 8% of total engagement (median 2). Facebook is 16% of posts and about 64% of total engagement. Median engagement is highest on LinkedIn (about 149), Instagram (about 134) and Facebook (about 74), and lowest on YouTube (0) and X (2).

**Media.** Posts with media have far higher median engagement than text-only posts (about 81 vs 3). Media, however, is completely absent for X in this dataset, so part of this gap is a platform effect. Inside Facebook, posts with media still outperform those without (median about 99 vs 49), and video (about 135) beats images (about 72). LinkedIn shows the same direction but a smaller gap.

**Text length and time.** Longer posts tend to have higher engagement, but text length also differs sharply by platform (YouTube and LinkedIn are long, X is short). Engagement rises with year, but the platform mix changes over time (LinkedIn and TikTok only start in 2024), so the trend cannot be read as a pure time effect. Weekday and month differences look small in medians.

**Data caveats.** `shareCount` is entirely missing for Instagram and YouTube and `commentCount` is partly missing for Facebook and LinkedIn; `videoplayCount` exists for only 886 posts. Because `social_engagement` is built from these counts, it is understated for platforms that do not report shares. `text_length` has extreme outliers (up to about 39,000 characters), and 82 posts have no text.

# 7. Bivariate analysis

Engagement is heavily skewed and clearly non-normal.

## 7.1 Assumption check

```{r normality}
set.seed(1)
shapiro.test(sample(fonterra$log_engagement, 5000))

ggplot(fonterra, aes(sample = log_engagement)) +
  stat_qq(alpha = 0.3) + stat_qq_line(colour = "#e07a5f") +
  labs(title = "Normal Q-Q plot of log(1 + engagement)") +
  theme_modern()
```

## 7.2 Correlation (numeric vs numeric)

```{r correlation}
cor_res <- fonterra |>
  select(social_engagement, text_length, word_count, year) |>
  correlation::correlation(method = "spearman", p_adjust = "holm")

cor_res |> as_tibble() |>
  select(Parameter1, Parameter2, rho, CI_low, CI_high, p, n_Obs) |>
  gt() |> fmt_number(c(rho, CI_low, CI_high), decimals = 2) |>
  fmt_scientific(p, decimals = 1) |>
  tab_header(title = "Spearman correlations (Holm-adjusted p)")

# Video plays vs engagement / likes (only posts with play counts)
video_df <- fonterra |> filter(!is.na(videoplayCount))
cor.test(video_df$social_engagement, video_df$videoplayCount, method = "spearman", exact = FALSE)
cor.test(video_df$likeCount,         video_df$videoplayCount, method = "spearman", exact = FALSE)

# Is the text-length relationship present within a single platform (X)?
x_df <- fonterra |> filter(platform == "Twitter/X")
cor.test(x_df$social_engagement, x_df$text_length, method = "spearman", exact = FALSE)

# Components of engagement
fonterra |>
  select(commentCount, shareCount, likeCount) |>
  correlation::correlation(method = "spearman", p_adjust = "holm") |>
  summary()
```


```{r correlation-plot}
fonterra |>
  select(social_engagement, text_length, word_count, year,
         likeCount, commentCount, shareCount) |>
  correlation::correlation(method = "spearman") |>
  summary(redundant = TRUE) |>
  plot()
```

## 7.3 ANOVA

```{r anova-platform}
# ANOVA 1: does log engagement differ by platform?

# Group means and SDs (log scale)
fonterra |>
  group_by(platform) |>
  summarise(n = n(), mean_log_eng = mean(log_engagement), sd_log_eng = sd(log_engagement),
            .groups = "drop") |>
  arrange(desc(mean_log_eng)) |>
  kable(digits = 2, caption = "Log engagement by platform")

# Welch ANOVA (does not assume equal variances, which is appropriate here)
welch_platform <- oneway.test(log_engagement ~ platform, data = fonterra, var.equal = FALSE)

tibble(F = unname(welch_platform$statistic),
       df_num = unname(welch_platform$parameter[1]),
       df_denom = unname(welch_platform$parameter[2]),
       p_value = format.pval(welch_platform$p.value, digits = 3, eps = 1e-16)) |>
  kable(digits = 2, caption = "Welch ANOVA: log engagement by platform")

# Classic ANOVA table and effect size (eta-squared)
aov_platform <- aov(log_engagement ~ platform, data = fonterra)
summary(aov_platform)
effectsize::eta_squared(aov_platform)

# Games-Howell post hoc test for all platform pairs (estimate = group2 minus group1, log scale)
gh_platform <- fonterra |> games_howell_test(log_engagement ~ platform)

gh_platform |>
  dplyr::select(group1, group2, estimate, conf.low, conf.high, p.adj, p.adj.signif) |>
  kable(digits = 3, caption = "Games-Howell post hoc test: platform pairs")
```

```{r anova-weekday}
# ANOVA 2: does log engagement differ by day of week?

# Group means and SDs (log scale)
fonterra |>
  group_by(day_of_week) |>
  summarise(n = n(), mean_log_eng = mean(log_engagement), sd_log_eng = sd(log_engagement),
            .groups = "drop") |>
  kable(digits = 2, caption = "Log engagement by day of week")

# Classic ANOVA table and effect size
aov_day <- aov(log_engagement ~ day_of_week, data = fonterra)
summary(aov_day)
effectsize::eta_squared(aov_day)   # the CI upper bound of 1.00 is normal (one-sided interval)

# Welch check: same conclusion without the equal-variance assumption
oneway.test(log_engagement ~ day_of_week, data = fonterra, var.equal = FALSE)
```

```{r anova-plot, fig.width=9, fig.height=5}
# Order platforms by mean log engagement so the plot matches the ANOVA table
platform_order <- fonterra |>
  group_by(platform) |>
  summarise(mean_log_eng = mean(log_engagement), .groups = "drop") |>
  arrange(desc(mean_log_eng)) |>
  pull(platform)

# Results pulled from the ANOVA chunks, so the plot subtitle always matches the output
eta_platform <- effectsize::eta_squared(aov_platform)[[2]][1]

# Plot 1: log engagement by platform (violin = distribution, box = quartiles, diamond = mean)
fonterra |>
  mutate(platform = factor(platform, levels = platform_order)) |>
  ggplot(aes(platform, log_engagement, fill = platform)) +
  geom_violin(show.legend = FALSE, alpha = 0.6) +
  geom_boxplot(width = 0.15, show.legend = FALSE, outlier.alpha = 0.1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3,
               fill = "white", show.legend = FALSE) +
  labs(title = "Engagement differs strongly by platform",
       subtitle = sprintf("Welch ANOVA: F(%.0f, %.1f) = %.1f, p < 0.001, eta-squared = %.2f (diamond = mean)",
                          welch_platform$parameter[1], welch_platform$parameter[2],
                          welch_platform$statistic, eta_platform),
       x = NULL, y = "log(1 + engagement)") +
  theme_modern()

# Results for the weekday ANOVA
aov_day_tab <- summary(aov_day)[[1]]
eta_day <- effectsize::eta_squared(aov_day)[[2]][1]

# Plot 2: log engagement by day of week (shows that differences are small)
fonterra |>
  ggplot(aes(day_of_week, log_engagement, fill = day_of_week)) +
  geom_boxplot(show.legend = FALSE, outlier.alpha = 0.1, alpha = 0.6) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3,
               fill = "white", show.legend = FALSE) +
  labs(title = "Engagement barely differs by day of week",
       subtitle = sprintf("ANOVA: F(%d, %d) = %.2f, p < 0.001, but eta-squared = %.3f (diamond = mean)",
                          aov_day_tab[["Df"]][1], aov_day_tab[["Df"]][2],
                          aov_day_tab[["F value"]][1], eta_day),
       x = NULL, y = "log(1 + engagement)") +
  theme_modern()
```

## 7.4 Chi-squared tests (Categorical vs categorical)

```{r chisq}
run_chisq <- function(data, a, b) {
  tab <- table(data[[a]], data[[b]])
  test <- chisq.test(tab)
  list(table = tab,
       test = test,
       min_expected = min(test$expected),
       cramers_v = effectsize::cramers_v(tab),
       std_resid = round(test$stdres, 1))
}

# (a) Platform vs having media
res1 <- run_chisq(fonterra, "platform", "media_present"); res1

# (b) Platform vs engagement level (High = above median of 5)
res2 <- run_chisq(fonterra, "platform", "engagement_level"); res2

# (c) Media type vs engagement level
res3 <- run_chisq(fonterra, "media_type", "engagement_level"); res3

# (d) Weekend vs engagement level
res4 <- run_chisq(fonterra, "day_type", "engagement_level"); res4
```

```{r chisq-plot}
fonterra |>
  count(platform, engagement_level) |>
  group_by(platform) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(platform, pct, fill = engagement_level)) +
  geom_col() +
  scale_y_continuous(labels = percent) +
  scale_fill_manual(values = c("#b8c4cc", "#2a6f97")) +
  labs(title = "Share of high-engagement posts by platform",
       x = NULL, y = NULL, fill = "Engagement") +
  theme_modern()
```

## 7.5 Results and Discussion

**Correlation:** Engagement is moderately and positively related to text length (Spearman rho about 0.45), word count (about 0.43) and year (about 0.49). Among the 886 posts with video play counts, plays and engagement are strongly related (rho about 0.74), and plays and likes similarly (about 0.73). Text length remains related to engagement inside X alone (rho about 0.42), so it is not purely a platform artifact. These are associations, not causal effects.

**ANOVA results (platform and day of week):** The ANOVA tests compare average engagement across groups. Because engagement is very uneven, the tests were run on log-transformed values.

Platform makes a big difference. Engagement differs strongly between platforms (F(5, 714.6) = 3689.4, p < 0.001). Platform alone explains about 61% of the differences in engagement, which is a very large effect. Every pair of platforms differs significantly. LinkedIn and Instagram perform best, then Facebook, then TikTok, X and YouTube.

Day of week hardly matters. The differences between days are statistically significant (F(6, 8994) = 6.09, p < 0.001) only because the dataset is large. They explain just 0.4% of the differences in engagement, so the day a post goes out has no practical effect.

Therefore, Platform is the main factor linked to engagement, so posting decisions should focus on where content is published, not on which day.

**Chi-squared.** Media use is strongly associated with platform (chi-squared about 6,553, df = 5, p < 0.001), which confirms the confounding between platform and media. Being a high-engagement post (above the median of 5) is also strongly associated with platform (chi-squared about 3,123, df = 5, p < 0.001). 

**Limitations.** Posts are not independent (same account, campaigns, reposts), the data is observational, the platform and year confounders are not controlled in bivariate tests, and missing counts are platform-specific.

# 8. Insights and recommendations

**Key insights**

1. **Most posts get little engagement, and a few get a lot.** The typical post receives about 5 interactions, and about 16% receive none. A small number of very popular posts, mostly on Facebook, pull the average up to about 60. This is why medians describe a typical post better than averages.

2. **Platform is the most important factor.** LinkedIn and Instagram have the highest typical engagement, followed by Facebook. TikTok is lower, and X and YouTube are lowest. Platform alone explains about 61% of the differences in engagement, and every pair of platforms is significantly different. Facebook produces a few viral posts, which give it about 64% of all engagement. X has 69% of the posts but only about 8% of the engagement.

3. **Replies on X lower its results.** About 40% of X posts are replies to customers, and these get much less engagement (median 1) than original posts (median 5). X should therefore not be judged by likes alone.

4. **Media helps, but it depends on the platform.** On Facebook, posts with images or video do better than text-only posts, and video does best. On LinkedIn, media may help, but the evidence is weak. On Instagram, video did worse than images and carousels. X, YouTube and TikTok could not be compared, because X does not record media and YouTube and TikTok are all video. So video is not the best choice everywhere.

5. **Timing matters very little.** Day of the week and month have almost no effect on engagement, and weekends are about the same as weekdays. Time of day was not tested in this report.

6. **Longer posts tend to get more engagement.** This holds even within X alone, so it is not only because some platforms use longer text. It shows a link, not a cause.

**Recommendations**

1. **Focus on LinkedIn, Instagram and Facebook** for brand and campaign content, where engagement is highest.

2. **Use X mainly for customer service and news,** and measure it by response quality and not by likes.

3. **Choose the format for each platform.** Use more video on Facebook, and test images and carousels on Instagram. Do not assume that video works everywhere.

4. **Study the most popular posts,** for example the top 1% on Facebook, to see which topics and formats worked and repeat them.

5. **Do not spend effort choosing the posting day.** Instead, test time of day in the next analysis, since the data has posting times.

6. **Improve the data.** Record shares for Instagram and YouTube, complete the comment counts, record media on X, and add follower numbers so platforms can be compared fairly.

**Limitations:** These results show associations in existing data and do not prove that a change would cause more engagement. Shares are not reported for Instagram and YouTube, so their engagement is understated.

**Next steps:** A regression that considers platform, media, text length and reply status together, and a check of which topics and tones get the most engagement.

# 9. GenAI Declaration

I used ChatGpt, Claude and Copilot AI as a supporting tool during this assignment. The tool was used for brainstorming, understanding and shortening R syntax, troubleshooting code, suggesting ways to structure the analysis, and improving explanations and writing.

I used GenAI as a supporting tool. I checked the suggested R code against the assignment requirements and ran the code in R using the supplied Fonterra dataset. I also inspected the data, outputs, statistical results, tables and visualisations myself and made the final decisions about data preparation, analysis and interpretation. Where GenAI suggestions were used, I verified that they were appropriate for the variables and statistical techniques covered in the course.
